### 2020-06-02 writeup/proof_examples.tex
sec B.1

%For the case $\sigma_1^2=\sigma_2^2=\sigma^2$, 
We define the function
\begin{align}
	\val(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
%\cor Under the setting of Lemma \ref{prop_model_shift_tight}, 
For the isotropic model with $\sigma_1^2=\sigma_2^2=\sigma^2$, using concentration for random vectors with i.i.d. entries, Lemma \ref{largedeviation}, we can obtain that $\val(\hat{B}; w_1, w_2)= \val(v) \cdot \left( 1+\OO(p^{-1/2+\e})\right)$. Hence the validation loss in \eqref{approxvalid} reduces to
\be\label{boundv-w}
\wt f(\hat B; v)=\left[N_2\cdot \val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
\ee
with high probability for any constant $\e>0$. \nc Thus for the following discussions, it suffices to focus on the behavior of $\val (v)$. Let $\hat w$ the minimizer of $\val(v)$. The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that the optimal ratio $\hat{w}$ is close to $1$. Then \eqref{boundv-w} will give that $|\hat v - \hat w|=\OO(p^{-1/2+\e_0/2+\e})$ whp.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
\end{itemize}
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result. 
\begin{lemma}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
For the isotropic model, the minimizer for $\val(v)$ satisfies
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{whp}\ee
	for some constant $C>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{lemma}
\begin{proof}
To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof. First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.

@@

For the rest of this section, we choose the parameters that satisfy the following relations: \be\label{choiceofpara}
pd^2 \sim \sigma^2 \sim 1,\quad p^{c_0}\kappa^2  \le \sigma^2 \le p^{1-\e_0-c_0} \kappa^2,
\ee
for some small constant $c_0>0$. We will explain below why we make this choice. Before that, we first prove the following result on the optimizer $\hat v$.
\begin{lemma}
For the isotropic model, we have
\be\label{hatv_add1} 
|\hat v - 1|= \OO\left(\cal E\right) \quad \text{whp}, \ee
where we used the notation
$$\cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 + 3\e}. $$
\end{lemma}
\begin{proof}
.......... In fact, from the proof of Lemma \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-\hat w| \le 2C\cal E$ for a large enough constant $C>1$, then $|\val'(w)|\gtrsim d^2$. Moreover, under the choice \eqref{choiceofpara} we have 
$$\val(w) =\OO(d^2),\quad \text{for}\quad   |w-\hat w|\le 2C\cal E.$$  
Thus we obtain that for $|w-\hat w|\ge 2C\cal E$,
$$\left|\val(w) - \val(\hat w)\right|\ge |\val(w)-\min(\val(w_1),\val(w_2))|\gtrsim d^2 \cal E \gtrsim \cal E \cdot \val(\hat w),$$
which leads to 
$$\wt f(\hat B; w) > \wt f(\hat B; \hat w) \quad \text{whp}.$$
Thus $w$ cannot be a minimizer of $\wt f(\hat B; v) $ by \eqref{boundv-w}, and we must have $|\hat v - \hat w|\le 2C\cal E$. Together with \eqref{hatw_add1}, we conclude \eqref{choiceofpara}.
\end{proof}

Inserting it into \eqref{eq_te_mtl_2task} and using a similar concentration result as in \eqref{boundv-w}, we get whp,
\begin{align}
\te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order. With estimate \eqref{eq_isometric}, we see that 
$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim \frac{p}{n_1+n_2}.$$
Hence we need to choose that $p\cdot d^2 \sim \sigma^2$. On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+2\e}\kappa^2  \ll d^2 \ll \kappa^2$. The above considerations lead to the following choices of parameters in \eqref{choiceofpara}.

Under this choice, we can write 
\be\label{simple1}
\begin{split}
\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \\ 
&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  
\end{split}
\ee
whp for some constant $\e>0$.

With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level. With slight abuse of notations, we shall write $\hat a_i$, $\hat b_k$ and $\hat M$ as $a_i$, $b_k$ and $M$, respectively, throughout the rest of this section.

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$. Then solving equations \eqref{eq_a2} and \eqref{eq_a3} with $\hat \lambda_i=1$, we get that
	\begin{align}
		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
	\end{align}
	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as 
\be\label{Deltavar}
\begin{split}
\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
\end{split}
\ee
with high probability, where 
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
	\end{align*}
	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next for the model shift bias
	$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of Lemma \ref{prop_model_shift_tight}) that
\be\label{Deltabeta} 
\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_\beta}{ \Delta_{\beta}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
	where 
	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
%\begin{align*}
%		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
%	\end{align*}
%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \ee	
%	Hence we obtain that
%	\begin{align*}
%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
%	\end{align*}
Note that 
 \be\label{var-beta}\te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta .\ee
Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.

\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} > \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is lower than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
	\[   pd^2  <  \sigma^2 \Phi(\rho_1, \rho_2)\cdot \left(\bigbrace{1 + \sqrt{\frac 1 {\rho_1}}}^{-4} - \oo(1)\right), \]
Plugging into $\rho_1>40$, we obtain the first statement of Proposition \ref{prop_dist_transition}.

\noindent{\bf Negative transfer.} On the other hand, if
\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} < \delta_{\beta}$, which implies that $\te(\hat{\beta}_t^{\MTL})$ is larger than $\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
	\[  p d^2  >  \sigma^2 \Phi(\rho_1, \rho_2) \cdot \left(\bigbrace{1 - \sqrt{\frac 1 {\rho_1}}}^{-4} +\oo(1)\right), \]
Plugging into $\rho_1>40$, we obtain the second statement of Proposition \ref{prop_dist_transition}.
\end{proof}

>>>>

%For the case $\sigma_1^2=\sigma_2^2=\sigma^2$, 
We define the function
\begin{align}
	\val(v) &= \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
%\cor Under the setting of Lemma \ref{prop_model_shift_tight}, 
For the isotropic model with $\sigma_1^2=\sigma_2^2=\sigma^2$, using concentration for random vectors with i.i.d. entries, Lemma \ref{largedeviation}, we can obtain that $\val(\hat{B}; w_1, w_2)= \val(v) \cdot \left( 1+\OO(p^{-1/2+\e})\right)$. Hence the validation loss in \eqref{approxvalid} reduces to
\be\label{boundv-w}
\wt f(\hat B; v)=\left[N_2\cdot \val(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
\ee
with high probability for any constant $\e>0$. \nc Thus for the following discussions, it suffices to focus on the behavior of $\val (v)$. Let $\hat w$ the minimizer of $\val(v)$. The proof will consist of two main steps.
\begin{itemize}
	\item First, we show that $\hat{w}$ is close to $1$, and then \eqref{boundv-w} implies that $\hat v$ is also close to 1.
	\item Second, we plug $\hat{v}$ back into $\te(\hat{\beta}_t^{\MTL})$ and use Lemma \ref{prop_model_shift_tight} to show the result.
\end{itemize}
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result. 
\begin{lemma}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order. 
For the isotropic model, the minimizer for $\val(v)$ satisfies
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{whp}\ee
	for some constant $C>0$.
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{lemma}
\begin{proof}
To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof. First it is easy to observe that $\val(w)< \val(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$.

@@

For the rest of this section, we choose the parameters that satisfy the following relations: \be\label{choiceofpara}
pd^2 \sim \sigma^2 \sim 1,\quad p^{-1+c_0} \sigma^2 \le \kappa^2  \le p^{-\e_0-c_0}\sigma^2 ,
\ee
for some small constant $c_0>0$. We will explain below why we make this choice. Before that, we first show the following estimate on the optimizer $\hat v$: with high probability,
%\begin{lemma}
%For the isotropic model, we have
\be\label{hatv_add1} 
|\hat v - 1|= \OO\left(\cal E\right), \quad \cal E:=\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2} + p^{-1/2 + \e_0 /2+ 2\e}. 
\ee
%\end{lemma}
%\begin{proof}
 In fact, from the proof of Lemma \ref{lem_hat_v} above, one can check that if $C\cal E \le |w-\hat w| \le 2C\cal E$ for a large enough constant $C>1$, then $|\val'(w)|\gtrsim p d^2$. Moreover, under the choice \eqref{choiceofpara} we have 
$$\val(w) =\OO(pd^2),\quad \text{for}\quad   |w-\hat w|\le 2C\cal E.$$  
Thus we obtain that for $|w-\hat w|\ge 2C\cal E$,
$$\left|\val(w) - \val(\hat w)\right|\ge |\val(w)-\min(\val(w_1),\val(w_2))|\gtrsim pd^2 \cal E \gtrsim \cal E \cdot \val(\hat w),$$
which leads to $\wt f(\hat B; w) > \wt f(\hat B; \hat w)$ whp by \eqref{boundv-w}. Thus $w$ cannot be a minimizer of $\wt f(\hat B; v) $, and we must have $|\hat v - \hat w|\le 2C\cal E$. Together with \eqref{hatw_add1}, we conclude \eqref{hatv_add1}.
%\end{proof}

Inserting \eqref{hatv_add1} into \eqref{eq_te_mtl_2task} and applying Lemma  \ref{largedeviation} to $(\beta_1-\hat v\beta_s)$ again, we get whp,
\begin{align}
\te(\hat{\beta}_t^{\MTL})&=(1+\OO(\cal E))\cdot \left[d^2 + \OO\left(\cal E^2 \kappa^2\right)\right] \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right]\nonumber\\ 
&+(1+\OO(\cal E))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \label{1Liso}
\end{align}
In order to study the phenomenon of bias-variance trade-off, we need the bias term with $d^2$ and the variance term with $\sigma^2$ to be of the same order. With estimate \eqref{eq_isometric}, we see that 
$$\tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \sim p,\quad \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \sim \frac{p}{n_1+n_2}.$$
Hence we need to choose that $p\cdot d^2 \sim \sigma^2$. On the other hand, we want the error term $\cal E^2 \kappa^2$ to be much smaller than $d^2$, which leads to the condition $p^{-1+\e_0+4\e}\kappa^2  \ll d^2 \ll \kappa^2$. The above considerations lead to the choices of parameters in \eqref{choiceofpara}. Moreover, under \eqref{choiceofpara} we can simplify \eqref{1Liso} to
\begin{align}
\te(\hat{\beta}_t^{\MTL})&=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\ 
&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
\end{align}
whp for some constant $\e>0$.

With \eqref{simple1} and Lemma \ref{prop_model_shift_tight}, we can prove Proposition \ref{prop_dist_transition}, which gives a transition threshold with respect to the ratio between the model bias and the noise level. With slight abuse of notations, we shall write $\hat a_i$, $\hat b_k$ and $\hat M$ as $a_i$, $b_k$ and $M$ throughout the rest of this section.

\begin{proof}[Proof of Proposition \ref{prop_dist_transition}]
	In the setting of Proposition \ref{prop_dist_transition}, we have $M = \Sigma_1^{1/2}\Sigma_2^{-1/2} = \id$. Then solving equations \eqref{eq_a2} and \eqref{eq_a3} with $\hat \lambda_i=1$, we get that
	\begin{align}
		 a_1 = \frac{\rho_1(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} ,\quad
		& a_2 = \frac{\rho_2(\rho_1 + \rho_2 - 1)}{(\rho_1 + \rho_2)^2} , \label{simplesovlea12}\\
		 a_3 = \frac{\rho_2}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}, \quad
		& a_4 = \frac{\rho_1}{(\rho_1 + \rho_2)(\rho_1 + \rho_2 - 1)}.\label{simplesovlea34}
	\end{align}
	Using Lemma \ref{lem_minv} and Lemma \ref{lem_cov_shift}, we can track the reduction of variance from $\hat{\beta}_t^{\MTL}$ to $\hat{\beta}_t^{\STL}$ as 
\be\label{Deltavar}
\begin{split}
\delta_{\vari}&:=\sigma^2  \bigtr{(X_2^{\top}X_2)^{-1} }  - (1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \\
&=\Delta_{\vari}\cdot (1+\OO(n^{-\e})) 
\end{split}
\ee
with high probability, where 
	\begin{align*}
		\Delta_{\vari} &\define \sigma^2 \bigbrace{\frac{1}{\rho_2 - 1} - \frac{1}{\rho_1 + \rho_2}\cdot\frac{1}{a_1+ a_2} } =\sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)}.
	\end{align*}
	%where we use equation \eqref{eq_a12} and Lemma \ref{lem_hat_v}.
	Next for the model shift bias
	$$\delta_\beta:=(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right], $$
	we can get from Lemma \ref{prop_model_shift_tight} (or rather the proof of it) that
\be\label{Deltabeta} 
\al_-^2(\rho_1) - \oo(1)  \le \frac{\delta_\beta}{ \Delta_{\beta}} \le \al_+^2(\rho_1) +  \oo(1) , \ee
	where 
	$$\Delta_{\beta}:=pd^2 \cdot \frac{\rho_1^2}{(\rho_1+\rho_2)^2}  \frac{1 + a_3 + a_4}{(a_1 + a_2)^2}= pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3}.$$	
%\begin{align*}
%		\Delta_{\beta} &\define \hat{v}^2 \bignorm{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1 (\beta_s - \hat{v}\beta_t)}^2 \\
%		&= d^2 \cdot \bignormFro{(\hat{v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}X_1^{\top}X_1}^2 + \bigo{p^{-1/2 + \varepsilon}d^2}
%	\end{align*}
%	Using Lemma \ref{prop_model_shift_tight}, we get an upper and lower bound on $\Delta_{\beta}$ as
%	\be\label{Deltabeta} \bigbrace{1 - \sqrt{\frac{1}{c_1}}}^4 \le \Delta_{\beta} / \bigbrace{p\cdot d^2 \cdot \frac{c_1^2}{(c_1+c_2)^2} \cdot \frac{1 + a_3 + a_4}{(a_1 + a_2)^2} + \bigo{p^{1/2+\e}d^2} } \le \bigbrace{1 + \sqrt{\frac{1}{c_1}}}^4. \ee	
%	Hence we obtain that
%	\begin{align*}
%		\frac{1 + a_3 + a_4}{(a_1 + a_2)^2}
%		= \frac{(c_1 + c_2)^3}{(c_1 + c_2 - 1)^3} + \bigo{p^{-1/2+\varepsilon}}.
%	\end{align*}
Note that 
 \be\label{var-beta}\te(\hat{\beta}_t^{\STL})-\te(\hat{\beta}_t^{\MTL}) =\delta_{\vari} - \delta_\beta .\ee
Then we can track its sign using \eqref{Deltavar} and \eqref{Deltabeta}.

\noindent{\bf Positive transfer.} With \eqref{Deltavar} and \eqref{Deltabeta}, we conclude that if
\be\label{upper101}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_+^2(\rho_1) +  \oo(1) \right) < \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} > \delta_{\beta}$, which implies $\te(\hat{\beta}_t^{\MTL})<\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper101} to
	\[  \frac{pd^2}{\sigma^2}  <   \Phi(\rho_1, \rho_2)\cdot \left( \al_+^2(\rho_1) +  \oo(1) \right)^{-1}, \]
Since $ \Psi(\beta_1,\beta_2)=pd^2/\sigma^2$, it gives the first statement of Proposition \ref{prop_dist_transition}.

\noindent{\bf Negative transfer.} On the other hand, if
\be\label{upper102}pd^2 \cdot \frac{\rho_1^2 (\rho_1+\rho_2)}{(\rho_1 + \rho_2 - 1)^3} \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right) > \sigma^2  \cdot \frac{\rho_1}{(\rho_2-1)(\rho_1 + \rho_2 -1)},\ee
	we have that $\delta_{\vari} < \delta_{\beta}$, which implies $\te(\hat{\beta}_t^{\MTL})>\te(\hat{\beta}_t^{\STL})$. We can simplify \eqref{upper102} to
	\[ \Psi(\beta_1,\beta_2)=\frac{ p d^2}{\sigma^2}  >  \Phi(\rho_1, \rho_2) \cdot \left( \al_-^2(\rho_1) -  \oo(1) \right)^{-1}, \]
which gives the second statement of Proposition \ref{prop_dist_transition}.
\end{proof}
